Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-07-04 prospects.tex
minor rewording of sentence baout sky localization and third generation detectors
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1233 ccdd05d5-56c1-461a-bf98-85f6876523b4
science infrastructure -> detector infrastructure
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1251 ccdd05d5-56c1-461a-bf98-85f6876523b4

We emphasize that any practical \GW\ search will include technical delays due
to light travel time between the detectors, science infrastructure, and the
selected data analysis strategy.  Figure~\ref{fig:earlywarning} must be understood
in the context of all of the potential sources of latency, some of which are avoidable
and some of which are not.

@@

It is infeasible to search hundreds of square degrees for a prompt counterpart.
For reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6~deg$^2$
\citep{2008arXiv0805.2366I}.  However, 
it is possible to reduce the localization uncertainty by only looking at
galaxies from a catalog that lie near the sky location and luminosity distance
estimate from the \GW{} signal~\citep{galaxy-catalog} as was done in S6/VSR3.
Within the expected Advanced \LIGO{} \textsc{ns}--\textsc{ns} horizon distance,
the number of galaxies that can produce a given signal amplitude is much larger
than in Initial \LIGO{} and thus the catalog will not be as useful
for downselecting pointings for most events. However, exceptional \GW{} sources will
necessarily be extremely nearby. Within this reduced volume there will be fewer
galaxies to consider for a given candidate and catalog completeness will be
less of a concern.  This should reduce the 90\% confidence area substantially.
Also future \GW{} detectors, should they be built, will improve the \SNR\ and
likewise the error box.

>>>>

We emphasize that any practical \GW\ search will include technical delays due
to light travel time between the detectors, detector infrastructure, and the
selected data analysis strategy.  Figure~\ref{fig:earlywarning} must be understood
in the context of all of the potential sources of latency, some of which are avoidable
and some of which are not.

@@

It is infeasible to search hundreds of square degrees for a prompt counterpart.
For reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6~deg$^2$
\citep{2008arXiv0805.2366I}.  However, 
it is possible to reduce the localization uncertainty by only looking at
galaxies from a catalog that lie near the sky location and luminosity distance
estimate from the \GW{} signal~\citep{galaxy-catalog} as was done in S6/VSR3.
Within the expected Advanced \LIGO{} \textsc{ns}--\textsc{ns} horizon distance,
the number of galaxies that can produce a given signal amplitude is much larger
than in Initial \LIGO{} and thus the catalog will not be as useful
for downselecting pointings for most events. However, exceptional \GW{} sources will
necessarily be extremely nearby. Within this reduced volume there will be fewer
galaxies to consider for a given candidate and catalog completeness will be
less of a concern.  This should reduce the 90\% confidence area substantially.
Proposed third generation \GW{} detectors would improve the \SNR\ and likewise
sky localization.
